\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-25 papers/jfp/8-engineering.tex
Work on S8.1

\noindent
Since tasks are polymorphic in \hs{f}, we can directly run them with the
callback \hs{fetchA1A2}. For example, the task description \hs{sprsh1}
from~\S\ref{sec-task} will return \hs{Just}~\hs{(Just}~\hs{30)} for the task
\cmd{B1 = A1 + A2}, \hs{Just}~\hs{Nothing} for the task \cmd{B2 = B1 * 2}
because \hs{fetchA1A2} failed, and simply \hs{Nothing} for the input \cmd{A1}.

@@

\noindent
With this approach we can define a \hs{MonadFail} build system that can handle
errors by aborting the build early.

\todo{AM}{Add a MonadFail build system.}

>>>>

\noindent
Since tasks are polymorphic in \hs{f}, we can directly run them with the
callback \hs{fetchA1A2}. For example, the task \cmd{B1 = A1 + A2} from
\hs{sprsh1} in~\S\ref{sec-task} returns \hs{Just}~\hs{30}, whereas the task
\cmd{B2 = B1 * 2} returns \hs{Nothing} because \hs{fetchA1A2} fails on \cmd{B1}.

@@

\noindent
With this approach we can implement a build system that accepts
\hs{Tasks}~\hs{MonadFail}~\hs{k}~\hs{v} and handles errors by aborting the
build early and returning
\hs{Either}~\hs{String}~\hs{(Store}~\hs{i}~\hs{k}~\hs{v)} instead of just
\hs{Store}~\hs{i}~\hs{k}~\hs{v} as in~\S\ref{sec-general-build}. One possible
implementation is based on introducing an extra \hs{Either}~\hs{String} layer
into the monad stack; while fairly direct it is also tedious, and hence we omit
it.

% \todo{AM}{Add a MonadFail build system.}
